\section{Phase 2: Necessity Theory for BLOM --- Why Exact Localization Cannot Be Obtained by Directly Localizing MINCO}
\label{sec:phase2_necessity}

This section establishes the mathematical necessity of BLOM.
The goal is to convert the motivation of BLOM from an intuitive statement into a rigorous obstruction theorem.
The central question is the following:

\begin{quote}
Can one preserve the sparse waypoint--duration parameterization of Phase~0 and the exact global optimality of the Phase~1 MINCO mother problem, while simultaneously obtaining exact finite local support of the coefficient map?
\end{quote}

The answer, under the Phase~0/1 parameterization, is negative.
More precisely, the loss of local support in MINCO is not an implementation artifact, but a structural consequence of the exact global optimality system.

Throughout this section, we adopt the notation of Phase~0 and Phase~1.
In particular,
\[
\theta=(q_1,\dots,q_{M-1},T_1,\dots,T_M)^\top,
\qquad
T_i>0,
\qquad
\mathcal T=\sum_{i=1}^{M}T_i,
\]
and the trajectory is represented segmentwise by
\[
p_i(\tau)=c_i^\top \beta_s(\tau),
\qquad
\tau\in[0,T_i],
\qquad
c_i\in\mathbb R^{2s},
\]
where
\[
\beta_s(\tau)=(1,\tau,\dots,\tau^{2s-1})^\top.
\]
Let
\[
c=(c_1^\top,\dots,c_M^\top)^\top\in\mathbb R^{2sM}.
\]
For notational convenience, we write the global coefficient system derived in Phase~1 as
\begin{equation}
\label{eq:phase2_global_system}
A(T)c^\star(q,T)=b(q,T),
\end{equation}
where \(A(T)\in\mathbb R^{2sM\times 2sM}\) is nonsingular and banded, and \(c^\star(q,T)\) denotes the unique globally optimal coefficient vector.

In the canonical setting of Phase~0 and Phase~1, one has \(s=4\), \(d_i=1\), and hence \(2s=8\).
However, most arguments in this section are stated for general \(s\), since the obstruction is structural rather than specific to minimum snap.

\subsection{Exact local support: definition and scope}
\label{subsec:phase2_local_support_def}

We first formalize what ``exact finite local support'' means in the present sparse waypoint parameterization.

Let
\[
\bar q := (q_1,\dots,q_{M-1})^\top \in \mathbb R^{M-1}
\]
denote the vector of interior waypoints.
For fixed \(T\), the exact optimal coefficient map is
\[
\bar q \longmapsto c^\star(\bar q,T)\in\mathbb R^{2sM}.
\]

\begin{definition}[Exact finite local support with respect to sparse waypoints]
\label{def:phase2_exact_local_support}
Fix \(T\).
We say that the exact optimal coefficient map has \emph{finite local support of half-bandwidth \(w\)} with respect to the sparse waypoint variables if, for every segment index \(i\in\{1,\dots,M\}\), there exists a function
\[
\Phi_i^{(T)}:\mathbb R^{|\mathcal N_w(i)|}\to\mathbb R^{2s}
\]
such that
\begin{equation}
\label{eq:phase2_local_map}
c_i^\star(\bar q,T)
=
\Phi_i^{(T)}\!\bigl((q_j)_{j\in \mathcal N_w(i)}\bigr),
\end{equation}
where
\[
\mathcal N_w(i)
:=
\{\,j\in\{1,\dots,M-1\}: |j-i|\le w\,\}.
\]
Equivalently, whenever \(c^\star\) is differentiable with respect to \(\bar q\),
\begin{equation}
\label{eq:phase2_local_support_jacobian}
\frac{\partial c_i^\star}{\partial q_j}(\bar q,T)=0
\qquad
\text{for all } |j-i|>w.
\end{equation}
If such a \(w\) exists independently of \(M\), we say that the exact optimal coefficient map has \emph{uniform finite local support}.
\end{definition}

\begin{remark}
\label{rem:phase2_scope_of_definition}
Definition~\ref{def:phase2_exact_local_support} is deliberately tied to the Phase~0/1 sparse parameterization by interior waypoints and segment durations.
This is the relevant notion for BLOM, whose purpose is precisely to preserve the sparse outer interface \(\theta=(q,T)\) while recovering locality.
\end{remark}

\subsection{The root cause of the loss of local support in MINCO}
\label{subsec:phase2_root_cause}

The first observation is that, once the exact global optimum is represented through the coefficient system \eqref{eq:phase2_global_system}, the sensitivity of \(c^\star\) with respect to the sparse waypoint variables is entirely determined by the inverse of the global banded matrix \(A(T)\).

In the canonical Phase~1 construction, the right-hand side is affine in the interior waypoints:
\begin{equation}
\label{eq:phase2_rhs_affine}
b(q,T)=b_0(T)+S_q \bar q,
\end{equation}
where \(S_q\in\mathbb R^{2sM\times(M-1)}\) is a fixed sparse selector matrix.
For \(d_i=1\), each interior waypoint enters exactly one scalar interpolation row, and therefore each column of \(S_q\) contains exactly one nonzero entry equal to \(1\).

\begin{lemma}[Exact coefficient sensitivity with respect to sparse waypoints]
\label{lem:phase2_exact_sensitivity}
Assume that \(A(T)\) is nonsingular.
Then, for every fixed \(T\),
\begin{equation}
\label{eq:phase2_exact_map}
c^\star(\bar q,T)=A(T)^{-1}\bigl(b_0(T)+S_q\bar q\bigr),
\end{equation}
and the Jacobian of the exact optimal coefficient map with respect to the interior waypoint vector is
\begin{equation}
\label{eq:phase2_jacobian_exact}
D_{\bar q}c^\star(\bar q,T)=A(T)^{-1}S_q.
\end{equation}
In particular, this Jacobian is independent of \(\bar q\).
\end{lemma}

\begin{proof}
Equation~\eqref{eq:phase2_exact_map} follows immediately from the nonsingularity of \(A(T)\) and the affine form \eqref{eq:phase2_rhs_affine}:
\[
c^\star(\bar q,T)
=
A(T)^{-1}b(q,T)
=
A(T)^{-1}\bigl(b_0(T)+S_q\bar q\bigr).
\]
Differentiating with respect to \(\bar q\) yields
\[
D_{\bar q}c^\star(\bar q,T)=A(T)^{-1}S_q,
\]
since \(A(T)\) and \(b_0(T)\) do not depend on \(\bar q\).
\end{proof}

\begin{remark}[Why banded \(A(T)\) does not imply local support]
\label{rem:phase2_banded_not_enough}
The matrix \(A(T)\) in \eqref{eq:phase2_global_system} is banded because the Euler--Lagrange and knot coupling conditions are local in the segment index.
However, the exact coefficient map is governed by \(A(T)^{-1}\), not by \(A(T)\) itself.
Therefore, the structural question relevant to local support is whether \(A(T)^{-1}S_q\) is finitely banded, not whether \(A(T)\) is banded.
\end{remark}

\subsection{Weak obstruction theorem: dense inverse implies loss of exact local support}
\label{subsec:phase2_weak_theorem}

We now state the first, weaker theorem.
It is already sufficient to justify the transition from exact global optimality to local optimality.

\begin{theorem}[Weak obstruction theorem]
\label{thm:phase2_weak_obstruction}
Fix \(T\), and assume that \(A(T)\) is nonsingular.
Suppose that the matrix
\[
A(T)^{-1}S_q \in \mathbb R^{2sM\times(M-1)}
\]
is not block-banded with any prescribed half-bandwidth \(w\).
Then the exact globally optimal coefficient map
\[
\bar q\longmapsto c^\star(\bar q,T)
\]
does not admit exact finite local support of half-bandwidth \(w\) in the sense of Definition~\ref{def:phase2_exact_local_support}.
\end{theorem}

\begin{proof}
Assume, to the contrary, that the exact optimal coefficient map has local support of half-bandwidth \(w\).
Then by Definition~\ref{def:phase2_exact_local_support}, whenever differentiable,
\[
\frac{\partial c_i^\star}{\partial q_j}(\bar q,T)=0
\qquad \text{for all } |j-i|>w.
\]
Equivalently, the Jacobian \(D_{\bar q}c^\star(\bar q,T)\) is block-banded with half-bandwidth \(w\).

By Lemma~\ref{lem:phase2_exact_sensitivity},
\[
D_{\bar q}c^\star(\bar q,T)=A(T)^{-1}S_q.
\]
Hence \(A(T)^{-1}S_q\) must also be block-banded with half-bandwidth \(w\), contradicting the assumption.
Therefore the exact optimal coefficient map cannot have exact finite local support of half-bandwidth \(w\).
\end{proof}

\begin{corollary}[Immediate consequence for MINCO]
\label{cor:phase2_minco_no_local_support}
If, for a given \(T\), the matrix \(A(T)^{-1}S_q\) has nonzero entries arbitrarily far from the block diagonal, then the exact MINCO coefficient map loses local support with respect to the sparse waypoint parameterization.
\end{corollary}

\begin{proof}
Apply Theorem~\ref{thm:phase2_weak_obstruction} for every candidate half-bandwidth \(w\).
\end{proof}

\begin{remark}[Interpretation]
\label{rem:phase2_interpretation}
Theorem~\ref{thm:phase2_weak_obstruction} is intentionally conditional.
It does not claim that every banded matrix has a dense inverse.
Rather, it states that \emph{once} the exact global optimality system produces a non-banded matrix \(A(T)^{-1}S_q\), exact finite local support becomes impossible.
This already explains why BLOM cannot be obtained by naively ``localizing'' the exact MINCO map while preserving exact global optimality.
\end{remark}

\subsection{From the weak theorem to a structural impossibility theorem}
\label{subsec:phase2_strong_theorem}

We next upgrade the previous result from a fixed-\(T\) statement to a structural impossibility theorem under the Phase~0/1 sparse parameterization.

Let
\[
\mathfrak S_{s}(T)
\]
denote the class of piecewise polynomials of degree at most \(2s-1\) on the partition induced by \(T\), and let
\[
\mathfrak A_{s}(q,T)
\subset \mathfrak S_s(T)
\]
denote the affine feasible subset satisfying the interpolation constraints, the prescribed endpoint jet, and the required continuity constraints from the global minimum-control problem.
By Phase~1, for every admissible \((q,T)\), the exact global minimum exists uniquely and is represented by a unique coefficient vector \(c^\star(q,T)\).

We now formalize the impossibility of combining the following three requirements:

1. exact global optimality in the Phase~1 MINCO mother problem,
2. the sparse outer parameterization \(\theta=(q,T)\),
3. uniform finite local support of the coefficient map.

\begin{theorem}[Impossibility of exact finite local support under the Phase~0/1 sparse parameterization]
\label{thm:phase2_strong_impossibility}
Assume the following:

\begin{enumerate}
    \item For every admissible pair \((q,T)\), the Phase~1 global minimum-control problem has a unique minimizer \(p^\star(\cdot;q,T)\), with coefficient vector \(c^\star(q,T)\in\mathbb R^{2sM}\).

    \item For every admissible \(T\), the coefficient vector is characterized by the exact global system
    \[
    A(T)c^\star(q,T)=b(q,T),
    \]
    with \(A(T)\) nonsingular and \(b(q,T)=b_0(T)+S_q\bar q\).

    \item There is no uniform half-bandwidth \(w\), independent of \(M\), such that
    \[
    A(T)^{-1}S_q
    \]
    is block-banded with half-bandwidth \(w\) for all admissible \(T\).
\end{enumerate}

Then there does not exist an exact coefficient representation
\begin{equation}
\label{eq:phase2_hypothetical_local_representation}
c_i^\star(q,T)
=
\Psi_i\!\bigl((q_j,T_j)_{j\in \mathcal N_w(i)}\bigr),
\qquad i=1,\dots,M,
\end{equation}
with a uniform half-bandwidth \(w\) independent of \(M\), that reproduces the exact global optimum for all admissible \((q,T)\).

Equivalently, under the sparse outer parameterization of Phase~0/1, one cannot simultaneously retain:

\begin{enumerate}
    \item exact global optimality,
    \item exact coefficient reproduction,
    \item uniform finite local support.
\end{enumerate}
\end{theorem}

\begin{proof}
Suppose, for contradiction, that there exists a representation of the form
\eqref{eq:phase2_hypothetical_local_representation} with a uniform half-bandwidth \(w\).
Fix any admissible \(T\).
Since the representation is exact, the coefficient vector generated by \eqref{eq:phase2_hypothetical_local_representation} must coincide with the unique globally optimal coefficient vector \(c^\star(q,T)\) for every admissible \(q\).
Hence, by differentiability, its Jacobian with respect to \(\bar q\) must satisfy the locality condition
\[
\frac{\partial c_i^\star}{\partial q_j}(q,T)=0
\qquad \text{whenever } |j-i|>w.
\]
Therefore \(D_{\bar q}c^\star(q,T)\) is block-banded with half-bandwidth \(w\).

On the other hand, by Lemma~\ref{lem:phase2_exact_sensitivity},
\[
D_{\bar q}c^\star(q,T)=A(T)^{-1}S_q.
\]
Thus \(A(T)^{-1}S_q\) must be block-banded with the same uniform half-bandwidth \(w\) for every admissible \(T\), contradicting assumption (3).
Therefore no such exact finite-local-support representation exists.
\end{proof}

\begin{remark}[What this theorem does and does not forbid]
\label{rem:phase2_scope_of_strong_theorem}
Theorem~\ref{thm:phase2_strong_impossibility} does \emph{not} say that no local trajectory representation can ever exist.
It only rules out exact finite-local-support representations that preserve the Phase~0/1 sparse outer variables and reproduce the exact global optimum of the Phase~1 mother problem.
Hence the theorem leaves open three possible routes:
\begin{enumerate}
    \item relax exact global optimality;
    \item enlarge the parameter set (for example, introduce additional knot-state variables);
    \item change the representation space itself.
\end{enumerate}
BLOM will follow the first route.
\end{remark}

\subsection{Consequences for BLOM}
\label{subsec:phase2_consequence_for_blom}

Theorems~\ref{thm:phase2_weak_obstruction} and \ref{thm:phase2_strong_impossibility} provide the exact logical transition from MINCO to BLOM.

\paragraph{Conclusion 1: direct localization of the exact MINCO map is impossible.}
Once the exact global optimum is encoded by a system of the form
\[
A(T)c^\star(q,T)=b(q,T),
\]
the sensitivity with respect to sparse waypoint variables is
\[
D_{\bar q}c^\star = A(T)^{-1}S_q.
\]
Therefore local support is controlled by the inverse operator, not by the local coupling pattern of \(A(T)\) itself.
If the inverse-induced sensitivity is not finitely banded, then any exact coefficient map must be globally coupled.

\paragraph{Conclusion 2: BLOM must relax exact global optimality.}
In order to recover locality while keeping the sparse outer variables \((q,T)\), BLOM cannot remain an exact globally optimal coefficient map.
Instead, BLOM must be defined through \emph{locally optimal} or \emph{windowwise optimal} subproblems.
This is not a heuristic choice, but a mathematically necessary relaxation.

\paragraph{Conclusion 3: Phase~2 is the logical bridge to Phase~3.}
Phase~3 will therefore not attempt to reproduce the exact MINCO coefficient map locally.
Instead, it will define a new map
\[
(q,T)\longmapsto c^{\mathrm{BLOM}}(q,T)
\]
through local optimization windows, and will study which properties of the exact MINCO map can be preserved after sacrificing exact global optimality.

\subsection{Canonical specialization to the Phase~0 setting}
\label{subsec:phase2_canonical_specialization}

For the canonical configuration of Phase~0 and Phase~1,
\[
s=4,\qquad d_i=1,
\]
each segment coefficient block satisfies
\[
c_i\in\mathbb R^8,
\]
and the global coefficient vector belongs to \(\mathbb R^{8M}\).
The global exact optimality system is
\[
A(T)c^\star(q,T)=b_0(T)+S_q\bar q,
\qquad
A(T)\in\mathbb R^{8M\times 8M},
\qquad
S_q\in\mathbb R^{8M\times(M-1)}.
\]
Hence the exact waypoint sensitivity is
\[
D_{\bar q}c^\star(q,T)=A(T)^{-1}S_q.
\]
Therefore, in the canonical minimum-snap case, the entire question of whether exact local support can hold is reduced to the structural sparsity, or lack thereof, of the matrix \(A(T)^{-1}S_q\).

\subsection{Roadmap implication}
\label{subsec:phase2_roadmap_implication}

Phase~2 identifies the precise mathematical obstruction that BLOM must circumvent:
\[
\boxed{
\text{exact global optimality}
\;+\;
\text{sparse waypoint parameterization}
\;\Longrightarrow\;
\text{inverse-induced global coupling}.
}
\]
Accordingly, the next phase will not attempt to preserve the exact map \(c^\star(q,T)\), but to construct a new locally computable map that preserves as much of the MINCO structure as possible while restoring finite local support.